Run models

### 2017-01-31 Code/run-models.Rmd
moved things and dup for local

#SET 2: Colorado, Connecticut, Delaware, Washington DC
save(r.All, le.calculations, file = "~/BlackWhiteMortalityGap/Results/results_set_2.Rdata") 
write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_2.csv")
write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_2.csv")
write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_2.csv")
write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_2.csv")
```

>>>>

#SET 2: Colorado, Connecticut, Delaware, Washington DC
save(r.All, le.calculations, file = "~/BW_results/results_set_2.Rdata") 
write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_2.csv")
write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_2.csv")
write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_2.csv")
write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_2.csv")
```
